A cross-benchmark comparison of Learning to Rank methods

### 2014-05-15 cikm_paper/paper.tex
begin mooie tabel :)

\documentclass{sig-alternate-2013}

\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{ACM International Conference on Information and Knowledge Management}{'14 Shanghai, China}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{A cross benchmark comparison of Learning to Rank methods}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Niek Tax\titlenote{affiliated with University of Twente, but written during his time at Avanade Netherlands B.V.}\\
       \affaddr{Avanade Netherlands B.V.}\\
       \affaddr{Versterkerstraat 6}\\
       \affaddr{1322 AP Almere}\\
       \affaddr{The Netherlands}
       \email{niek.tax@avanade.com}
% 2nd. author
\alignauthor
Djoerd Hiemstra\\
       \affaddr{University of Twente}\\
       \affaddr{P.O. Box 217}\\
       \affaddr{7500 AE Enschede}\\
       \affaddr{The Netherlands}
       \email{d.hiemstra@utwente.nl}
% 3rd. author
\alignauthor
Sander Bockting\\
       \affaddr{Avanade Netherlands B.V.}\\
       \affaddr{Versterkerstraat 6}\\
       \affaddr{1322 AP Almere}\\
       \affaddr{The Netherlands}
       \email{sander.bockting@avanade.com}
}

@@

\keywords{, }

@@

\section{The {\secit Body} of The Paper}

\subsection{Type Changes and {\subsecit Special} Characters}
\label{chap:cross_comparison}
As we have seen in Chapter~\ref{chap:benchmark_results}, the evaluation of Learning-to-Rank methods is spread over several benchmark datasets. However, as the Learning-to-Rank methods evaluated differs between benchmarks, no single benchmark comparison can be regarded as a conclusive argument on which Learning-to-Rank method is most accurate.\\

@@

\begin{table}[!h]
\begin{tabular}{l|l|l}
Benchmark & Paper & \# of forward references \\
\hline
LETOR 1.0 \& 2.0 & Liu et al. \cite{Liu2007b} & 307\\
LETOR 3.0 & Qin et al. \cite{Qin2010} & 105\\
Yahoo! Learning to Rank Challenge & Chapelle et al. \cite{Chapelle2011a} & 102\\
AOL dataset & Pass et al. \cite{Pass2006} & 339\\
WCL2R & Alc{\^a}ntara et al. \cite{Alcantara2010} & 2\\
\end{tabular}
\caption{Forward references of Learning-to-Rank benchmark papers}
\label{tbl:ltr_benchmark_forref}
\end{table}

@@

\begin{table}[!h]
\begin{tabular}{l|l}
Benchmark & Google scholar search results \\
\hline
LETOR 4.0 & 75 results \\
MSLR-web10k & 16 results \\
MSLR-web30k & 15 results \\
Yandex Internet Mathematics Competition & 1 result \\ 
\end{tabular}
\caption{Google scholar search results for Learning-to-Rank benchmarks}
\label{tbl:ltr_benchmark_searchres}
\end{table}

@@

\begin{table}[!h!p]

@@

\end{table}

@@

\begin{figure}[!h]
\includegraphics[scale=0.285]{gfx/ndcg3_winnum}
\caption{NDCG@3 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg3}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[scale=0.285]{gfx/ndcg5_winnum}
\caption{NDCG@5 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg5}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[scale=0.285]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg10}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[scale=0.285]{gfx/map_winnum}
\caption{MAP comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_map}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[scale=0.33]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
\section{Raw Data for NDCG@3 Comparison}
\label{app:norm_winnum_NDCG3}

\begin{table}
\begin{tabular}{l|l|l}
Method & Normalised Winning Number & \# of datasets \\
\hline
AdaRank-MAP & 0.34862385 & 12 \\ 
AdaRank-NDCG & 0.30733945 & 12 \\ 
ApproxNDCG & 0.79487179 & 1 \\ 
BagBoo & 0.84782609 & 2 \\ 
BL-MART & 0.95238095 & 2 \\ 
BoltzRank-Pair & 0.83333333 & 4 \\ 
BoltzRank-Single & 0.75490196 & 4 \\ 
BT & 0.72727273 & 3 \\ 
CoList & 1.00000000 & 1 \\ 
DCMP & 0.54591837 & 9 \\ 
EnergyNDCG & 0.36363636 & 2 \\ 
FBPCRank & 0.41463415 & 3 \\ 
FenchelRank & 0.77419355 & 5 \\ 
FocusedBoost & 0.37500000 & 2 \\ 
FocusedNet & 0.45833333 & 2 \\ 
FocusedSVM & 0.25000000 & 2 \\ 
FRank & 0.30845771 & 11 \\ 
FSMRank & 0.83333333 & 4 \\ 
FSMSVM & 0.22916667 & 4 \\ 
GAS-E & 0.37500000 & 4 \\ 
GPRank & 0.87096774 & 3 \\ 
GroupCE & 0.73118280 & 3 \\ 
GroupMLE & 0.52688172 & 3 \\ 
IntervalRank & 0.58974359 & 1 \\ 
IPRank & 0.93548387 & 3 \\ 
KL-CRF & 0.59459459 & 2 \\ 
LambdaMART & 0.57142857 & 2 \\ 
LambdaNeuralRank & 1.00000000 & 1 \\ 
LambdaRank & 0.20000000 & 1 \\ 
LARF & 0.98924731 & 3 \\ 
Linear Regression & 0.07142857 & 9 \\ 
ListMLE & 0.00000000 & 1 \\ 
ListNet & 0.44954128 & 12 \\ 
ListReg & 0.73118280 & 3 \\ 
LRUF & 0.98230088 & 4 \\ 
MHR & 0.75000000 & 1 \\ 
NewLoss & 0.51612903 & 3 \\ 
OWPC & 0.65000000 & 6 \\ 
PERF-MAP & 0.38938053 & 4 \\ 
RankBoost & 0.32110092 & 12 \\ 
RankELM (pairwise) & 0.61538462 & 1 \\ 
RankELM (pointwise) & 0.69230769 & 1 \\ 
RankNet & 0.18867925 & 1 \\ 
RankSVM & 0.30097087 & 12 \\ 
RankSVM-Primal & 0.39204545 & 8 \\ 
RankSVM-Struct & 0.35204082 & 9 \\ 
REG-SHF-SDCG & 0.38461538 & 1 \\ 
Ridge Regression & 0.40880503 & 7 \\ 
RSRank & 0.57291667 & 4 \\ 
SmoothRank & 0.60377358 & 7 \\ 
SoftRank & 0.23076923 & 1 \\ 
SortNet & 0.25000000 & 2 \\ 
SparseRank & 0.82242991 & 4 \\ 
SVMMAP & 0.28930818 & 7 \\ 
TGRank & 0.54166667 & 4 \\ 
TM & 0.59090909 & 3 \\
\end{tabular}
\caption{Raw data of Normalised Winning Number comparison on NDCG@3}
\label{tab:raw_data_norm_winnum_NDCG3}
\end{table}

@@

\begin{table}
\begin{tabular}{l|l|l}
Method & Normalised Winning Number & \# of datasets \\
\hline
AdaRank-MAP & 0.3883929 & 12 \\ 
AdaRank-NDCG & 0.3258929 & 12 \\ 
ApproxNDCG & 0.7500000 & 1 \\ 
BagBoo & 0.8400000 & 1 \\ 
BL-MART & 0.7200000 & 1 \\ 
BoltzRank-Pair & 0.8349515 & 4 \\ 
BoltzRank-Single & 0.7184466 & 4 \\ 
BT & 0.7878788 & 3 \\ 
C-CRF & 0.9500000 & 2 \\ 
DCMP & 0.5078534 & 9 \\ 
EnergyNDCG & 0.3777778 & 2 \\ 
FBPCRank & 0.5529412 & 3 \\ 
FenchelRank & 0.7500000 & 5 \\ 
FocusedBoost & 0.4545455 & 2 \\ 
FocusedNet & 0.6363636 & 2 \\ 
FocusedSVM & 0.2727273 & 2 \\ 
FPRank & 0.9000000 & 1 \\ 
FRank & 0.2849462 & 10 \\ 
FSMRank & 0.8775510 & 4 \\ 
FSMSVM & 0.4081633 & 4 \\ 
GAS-E & 0.4693878 & 4 \\ 
GPRank & 0.7252747 & 3 \\ 
IntervalRank & 0.3750000 & 1 \\ 
IPRank & 0.8131868 & 3 \\ 
Kernel-PCA & 0.2857143 & 3 \\ 
KL-CRF & 0.5789474 & 2 \\ 
LambdaNeuralRank & 1.0000000 & 1 \\ 
LambdaRank & 0.2000000 & 1 \\ 
LARF & 0.9890110 & 3 \\ 
Linear Regression & 0.1099476 & 9 \\ 
ListNet & 0.4910714 & 12 \\ 
ListReg & 0.6923077 & 3 \\ 
LRUF & 0.9816514 & 4 \\ 
MHR & 0.6000000 & 1 \\ 
NewLoss & 0.4285714 & 3 \\ 
PERF-MAP & 0.2660550 & 4 \\ 
Q.D.KNN & 0.3205128 & 3 \\ 
RankAggNDCG & 0.5000000 & 3 \\ 
RankBoost & 0.2794118 & 10 \\ 
RankDE & 0.5384615 & 1 \\ 
RankELM (pairwise) & 0.6500000 & 1 \\ 
RankELM (pointwise) & 0.7000000 & 1 \\ 
RankNet & 0.2857143 & 3 \\ 
Rank-PMBGP & 0.7692308 & 1 \\ 
RankSVM & 0.3612565 & 11 \\ 
RankSVM-Primal & 0.4508671 & 8 \\ 
RankSVM-Struct & 0.4136126 & 9 \\ 
RCP & 0.5757576 & 3 \\ 
REG-SHF-SDCG & 0.4500000 & 1 \\ 
Ridge Regression & 0.3333333 & 7 \\ 
RSRank & 0.5306122 & 4 \\ 
SmoothRank & 0.6339869 & 7 \\ 
SoftRank & 0.2750000 & 1 \\ 
SortNet & 0.5147059 & 4 \\ 
SparseRank & 0.8173077 & 4 \\ 
SVD-RankBoost & 0.2727273 & 3 \\ 
SVMMAP & 0.3801170 & 8 \\ 
SwarmRank & 0.1538462 & 1 \\ 
TGRank & 0.6122449 & 4 \\ 
TM & 0.7575758 & 3 \\ 
\end{tabular}
\caption{Raw data of Normalised Winning Number comparison on NDCG@5}
\label{tab:raw_data_norm_winnum_NDCG5}
\end{table}

@@

\begin{table}
\begin{tabular}{l|l|l}
Method & Normalised Winning Number & \# of datasets \\
\hline
AdaRank-MAP & 0.36480687 & 13 \\ 
AdaRank-NDCG & 0.31578947 & 16 \\ 
ADMM & 0.44444444 & 1 \\ 
ApproxNDCG & 0.86111111 & 1 \\ 
Best Single Feature & 0.16149068 & 8 \\ 
CA & 0.65217391 & 4 \\ 
CoList & 0.16666667 & 1 \\ 
Consistent-RankCosine & 0.76923077 & 2 \\ 
DCMP & 0.58883249 & 9 \\ 
DirectRank & 0.92307692 & 2 \\ 
EnergyNDCG & 0.41463415 & 2 \\ 
FenchelRank & 0.76229508 & 5 \\ 
FocusedBoost & 0.68627451 & 2 \\ 
FocusedNet & 0.86274510 & 2 \\ 
FocusedSVM & 0.60784314 & 2 \\ 
FRank & 0.30288462 & 11 \\ 
FSMRank & 0.86206897 & 5 \\ 
FSMSVM & 0.54255319 & 4 \\ 
GAS-E & 0.45744681 & 4 \\ 
GP & 0.66666667 & 2 \\ 
GPRank & 0.65909091 & 3 \\ 
GRankRLS & 0.28947368 & 2 \\ 
GroupCE & 0.72727273 & 3 \\ 
GroupMLE & 0.62500000 & 3 \\ 
IPRank & 0.79545455 & 3 \\ 
LAC-MR-OR & 0.66666667 & 2 \\ 
LambdaMART & 1.00000000 & 1 \\ 
LambdaNeuralRank & 1.00000000 & 1 \\ 
LambdaRank & 0.57142857 & 2 \\ 
LARF & 0.98863636 & 3 \\ 
Linear Regression & 0.08287293 & 8 \\ 
ListMLE & 0.02127660 & 4 \\ 
ListNet & 0.59821429 & 12 \\ 
LRUF & 0.98181818 & 4 \\ 
MHR & 0.62500000 & 1 \\ 
NewLoss & 0.39772727 & 3 \\ 
PERF-MAP & 0.20000000 & 4 \\ 
Q.D.KNN & 0.50000000 & 3 \\ 
RandomForest & 0.42236025 & 8 \\ 
RankAggNDCG & 0.87837838 & 3 \\ 
RankBoost & 0.39357430 & 17 \\ 
RankDE & 0.18181818 & 1 \\ 
RankELM (pairwise) & 0.69444444 & 1 \\ 
RankELM (pointwise) & 0.80555556 & 1 \\ 
RankNet & 0.59154930 & 5 \\ 
Rank-PMBGP & 0.27272727 & 1 \\ 
RankRLS & 0.36842105 & 2 \\ 
RankSVM & 0.44957983 & 17 \\ 
RankSVM-Primal & 0.45911950 & 7 \\ 
RankSVM-Struct & 0.44670051 & 9 \\ 
RCP & 0.74074074 & 3 \\ 
Ridge Regression & 0.36477987 & 7 \\ 
RSRank & 0.62765957 & 4 \\ 
SmoothGrad & 0.38461538 & 2 \\ 
SmoothRank & 0.64150943 & 7 \\ 
SoftRank & 0.61111111 & 1 \\ 
SortNet & 0.56666667 & 4 \\ 
SparseRank & 0.79439252 & 4 \\ 
SVD-RankBoost & 0.55555556 & 3 \\ 
SVMMAP & 0.35911602 & 8 \\ 
SwarmRank & 0.09090909 & 1 \\ 
TGRank & 0.50000000 & 4 \\
\end{tabular}
\caption{Raw data of Normalised Winning Number comparison on NDCG@10}
\label{tab:raw_data_norm_winnum_NDCG10}
\end{table}

>>>>

\documentclass{sig-alternate-2013}
\usepackage{longtable}
\usepackage{booktabs}
\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{ACM International Conference on Information and Knowledge Management}{'14 Shanghai, China}
\CopyrightYear{2014} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{A cross-benchmark comparison of Learning to Rank methods}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Niek Tax\titlenote{author is affiliated with the University of Twente, but this paper written during his time at Avanade Netherlands B.V.}\\
       \affaddr{Avanade Netherlands B.V.}\\
       \affaddr{Versterkerstraat 6}\\
       \affaddr{1322 AP Almere}\\
       \affaddr{The Netherlands}
       \email{niek.tax@avanade.com}
% 2nd. author
\alignauthor
Djoerd Hiemstra\\
       \affaddr{University of Twente}\\
       \affaddr{P.O. Box 217}\\
       \affaddr{7500 AE Enschede}\\
       \affaddr{The Netherlands}
       \email{d.hiemstra@utwente.nl}
% 3rd. author
\alignauthor
Sander Bockting\\
       \affaddr{Avanade Netherlands B.V.}\\
       \affaddr{Versterkerstraat 6}\\
       \affaddr{1322 AP Almere}\\
       \affaddr{The Netherlands}
       \email{sander.bockting@avanade.com}
}

@@

\keywords{}

@@

\section{Problem Statement \& Research Question}
\label{chap:cross_comparison}
Evaluation of Learning-to-Rank methods is spread over several benchmark datasets. However, as the Learning-to-Rank methods evaluated differs between benchmarks, no single benchmark comparison can be regarded as a conclusive argument on which Learning-to-Rank method is most accurate.\\

@@

\begin{table}[!h]
\begin{tabular}{p{3.2cm}|l|p{1.8cm}}
Benchmark & Paper & \# of forward references \\
\hline
LETOR 1.0 \& 2.0 & Liu et al. \cite{Liu2007b} & 307\\
LETOR 3.0 & Qin et al. \cite{Qin2010} & 105\\
Yahoo! Learning to Rank Challenge & Chapelle et al. \cite{Chapelle2011a} & 102\\
AOL dataset & Pass et al. \cite{Pass2006} & 339\\
WCL2R & Alc{\^a}ntara et al. \cite{Alcantara2010} & 2\\
\end{tabular}
\caption{Forward references of Learning-to-Rank benchmark papers}
\label{tbl:ltr_benchmark_forref}
\end{table}

@@

\begin{table}[!h]
\begin{tabular}{p{4.2cm}|p{2.5cm}}
Benchmark & Google scholar search results \\
\hline
LETOR 4.0 & 75 results \\
MSLR-web10k & 16 results \\
MSLR-web30k & 15 results \\
Yandex Internet Mathematics Competition & 1 result \\ 
\end{tabular}
\caption{Google scholar search results for Learning-to-Rank benchmarks}
\label{tbl:ltr_benchmark_searchres}
\end{table}

@@

\begin{table*}[!h!p]

@@

\end{table*}

@@

\begin{figure*}[!h]
\includegraphics[scale=0.285]{gfx/ndcg3_winnum}
\caption{NDCG@3 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg3}
\end{figure*}

@@

\begin{figure*}[!h]
\includegraphics[scale=0.285]{gfx/ndcg5_winnum}
\caption{NDCG@5 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg5}
\end{figure*}

@@

\begin{figure*}[!h]
\includegraphics[scale=0.285]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg10}
\end{figure*}

@@

\begin{figure*}[!h]
\includegraphics[scale=0.285]{gfx/map_winnum}
\caption{MAP comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_map}
\end{figure*}

@@

\begin{figure*}[!h]
\includegraphics[scale=0.33]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure*}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{Bibliography}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
\section{Raw Data for NDCG@3 Comparison}
\label{app:norm_winnum_NDCG3}

\begin{table*}
\begin{tabular}{l|l|l}
Method & Normalised Winning Number & \# of datasets \\
\hline
AdaRank-MAP & 0.34862385 & 12 \\ 
AdaRank-NDCG & 0.30733945 & 12 \\ 
ApproxNDCG & 0.79487179 & 1 \\ 
BagBoo & 0.84782609 & 2 \\ 
BL-MART & 0.95238095 & 2 \\ 
BoltzRank-Pair & 0.83333333 & 4 \\ 
BoltzRank-Single & 0.75490196 & 4 \\ 
BT & 0.72727273 & 3 \\ 
CoList & 1.00000000 & 1 \\ 
DCMP & 0.54591837 & 9 \\ 
EnergyNDCG & 0.36363636 & 2 \\ 
FBPCRank & 0.41463415 & 3 \\ 
FenchelRank & 0.77419355 & 5 \\ 
FocusedBoost & 0.37500000 & 2 \\ 
FocusedNet & 0.45833333 & 2 \\ 
FocusedSVM & 0.25000000 & 2 \\ 
FRank & 0.30845771 & 11 \\ 
FSMRank & 0.83333333 & 4 \\ 
FSMSVM & 0.22916667 & 4 \\ 
GAS-E & 0.37500000 & 4 \\ 
GPRank & 0.87096774 & 3 \\ 
GroupCE & 0.73118280 & 3 \\ 
GroupMLE & 0.52688172 & 3 \\ 
IntervalRank & 0.58974359 & 1 \\ 
IPRank & 0.93548387 & 3 \\ 
KL-CRF & 0.59459459 & 2 \\ 
LambdaMART & 0.57142857 & 2 \\ 
LambdaNeuralRank & 1.00000000 & 1 \\ 
LambdaRank & 0.20000000 & 1 \\ 
LARF & 0.98924731 & 3 \\ 
Linear Regression & 0.07142857 & 9 \\ 
ListMLE & 0.00000000 & 1 \\ 
ListNet & 0.44954128 & 12 \\ 
ListReg & 0.73118280 & 3 \\ 
LRUF & 0.98230088 & 4 \\ 
MHR & 0.75000000 & 1 \\ 
NewLoss & 0.51612903 & 3 \\ 
OWPC & 0.65000000 & 6 \\ 
PERF-MAP & 0.38938053 & 4 \\ 
RankBoost & 0.32110092 & 12 \\ 
RankELM (pairwise) & 0.61538462 & 1 \\ 
RankELM (pointwise) & 0.69230769 & 1 \\ 
RankNet & 0.18867925 & 1 \\ 
RankSVM & 0.30097087 & 12 \\ 
RankSVM-Primal & 0.39204545 & 8 \\ 
RankSVM-Struct & 0.35204082 & 9 \\ 
REG-SHF-SDCG & 0.38461538 & 1 \\ 
Ridge Regression & 0.40880503 & 7 \\ 
RSRank & 0.57291667 & 4 \\ 
SmoothRank & 0.60377358 & 7 \\ 
SoftRank & 0.23076923 & 1 \\ 
SortNet & 0.25000000 & 2 \\ 
SparseRank & 0.82242991 & 4 \\ 
SVMMAP & 0.28930818 & 7 \\ 
TGRank & 0.54166667 & 4 \\ 
TM & 0.59090909 & 3 \\
\end{tabular}
\caption{Raw data of Normalised Winning Number comparison on NDCG@3}
\label{tab:raw_data_norm_winnum_NDCG3}
\end{table*}

@@

\begin{table*}
\begin{tabular}{l|l|l}
Method & Normalised Winning Number & \# of datasets \\
\hline
AdaRank-MAP & 0.3883929 & 12 \\ 
AdaRank-NDCG & 0.3258929 & 12 \\ 
ApproxNDCG & 0.7500000 & 1 \\ 
BagBoo & 0.8400000 & 1 \\ 
BL-MART & 0.7200000 & 1 \\ 
BoltzRank-Pair & 0.8349515 & 4 \\ 
BoltzRank-Single & 0.7184466 & 4 \\ 
BT & 0.7878788 & 3 \\ 
C-CRF & 0.9500000 & 2 \\ 
DCMP & 0.5078534 & 9 \\ 
EnergyNDCG & 0.3777778 & 2 \\ 
FBPCRank & 0.5529412 & 3 \\ 
FenchelRank & 0.7500000 & 5 \\ 
FocusedBoost & 0.4545455 & 2 \\ 
FocusedNet & 0.6363636 & 2 \\ 
FocusedSVM & 0.2727273 & 2 \\ 
FPRank & 0.9000000 & 1 \\ 
FRank & 0.2849462 & 10 \\ 
FSMRank & 0.8775510 & 4 \\ 
FSMSVM & 0.4081633 & 4 \\ 
GAS-E & 0.4693878 & 4 \\ 
GPRank & 0.7252747 & 3 \\ 
IntervalRank & 0.3750000 & 1 \\ 
IPRank & 0.8131868 & 3 \\ 
Kernel-PCA & 0.2857143 & 3 \\ 
KL-CRF & 0.5789474 & 2 \\ 
LambdaNeuralRank & 1.0000000 & 1 \\ 
LambdaRank & 0.2000000 & 1 \\ 
LARF & 0.9890110 & 3 \\ 
Linear Regression & 0.1099476 & 9 \\ 
ListNet & 0.4910714 & 12 \\ 
ListReg & 0.6923077 & 3 \\ 
LRUF & 0.9816514 & 4 \\ 
MHR & 0.6000000 & 1 \\ 
NewLoss & 0.4285714 & 3 \\ 
PERF-MAP & 0.2660550 & 4 \\ 
Q.D.KNN & 0.3205128 & 3 \\ 
RankAggNDCG & 0.5000000 & 3 \\ 
RankBoost & 0.2794118 & 10 \\ 
RankDE & 0.5384615 & 1 \\ 
RankELM (pairwise) & 0.6500000 & 1 \\ 
RankELM (pointwise) & 0.7000000 & 1 \\ 
RankNet & 0.2857143 & 3 \\ 
Rank-PMBGP & 0.7692308 & 1 \\ 
RankSVM & 0.3612565 & 11 \\ 
RankSVM-Primal & 0.4508671 & 8 \\ 
RankSVM-Struct & 0.4136126 & 9 \\ 
RCP & 0.5757576 & 3 \\ 
REG-SHF-SDCG & 0.4500000 & 1 \\ 
Ridge Regression & 0.3333333 & 7 \\ 
RSRank & 0.5306122 & 4 \\ 
SmoothRank & 0.6339869 & 7 \\ 
SoftRank & 0.2750000 & 1 \\ 
SortNet & 0.5147059 & 4 \\ 
SparseRank & 0.8173077 & 4 \\ 
SVD-RankBoost & 0.2727273 & 3 \\ 
SVMMAP & 0.3801170 & 8 \\ 
SwarmRank & 0.1538462 & 1 \\ 
TGRank & 0.6122449 & 4 \\ 
TM & 0.7575758 & 3 \\ 
\end{tabular}
\caption{Raw data of Normalised Winning Number comparison on NDCG@5}
\label{tab:raw_data_norm_winnum_NDCG5}
\end{table*}

@@

\begin{table*}
\begin{tabular}{l|l|l}
Method & Normalised Winning Number & \# of datasets \\
\hline
AdaRank-MAP & 0.36480687 & 13 \\ 
AdaRank-NDCG & 0.31578947 & 16 \\ 
ADMM & 0.44444444 & 1 \\ 
ApproxNDCG & 0.86111111 & 1 \\ 
Best Single Feature & 0.16149068 & 8 \\ 
CA & 0.65217391 & 4 \\ 
CoList & 0.16666667 & 1 \\ 
Consistent-RankCosine & 0.76923077 & 2 \\ 
DCMP & 0.58883249 & 9 \\ 
DirectRank & 0.92307692 & 2 \\ 
EnergyNDCG & 0.41463415 & 2 \\ 
FenchelRank & 0.76229508 & 5 \\ 
FocusedBoost & 0.68627451 & 2 \\ 
FocusedNet & 0.86274510 & 2 \\ 
FocusedSVM & 0.60784314 & 2 \\ 
FRank & 0.30288462 & 11 \\ 
FSMRank & 0.86206897 & 5 \\ 
FSMSVM & 0.54255319 & 4 \\ 
GAS-E & 0.45744681 & 4 \\ 
GP & 0.66666667 & 2 \\ 
GPRank & 0.65909091 & 3 \\ 
GRankRLS & 0.28947368 & 2 \\ 
GroupCE & 0.72727273 & 3 \\ 
GroupMLE & 0.62500000 & 3 \\ 
IPRank & 0.79545455 & 3 \\ 
LAC-MR-OR & 0.66666667 & 2 \\ 
LambdaMART & 1.00000000 & 1 \\ 
LambdaNeuralRank & 1.00000000 & 1 \\ 
LambdaRank & 0.57142857 & 2 \\ 
LARF & 0.98863636 & 3 \\ 
Linear Regression & 0.08287293 & 8 \\ 
ListMLE & 0.02127660 & 4 \\ 
ListNet & 0.59821429 & 12 \\ 
LRUF & 0.98181818 & 4 \\ 
MHR & 0.62500000 & 1 \\ 
NewLoss & 0.39772727 & 3 \\ 
PERF-MAP & 0.20000000 & 4 \\ 
Q.D.KNN & 0.50000000 & 3 \\ 
RandomForest & 0.42236025 & 8 \\ 
RankAggNDCG & 0.87837838 & 3 \\ 
RankBoost & 0.39357430 & 17 \\ 
RankDE & 0.18181818 & 1 \\ 
RankELM (pairwise) & 0.69444444 & 1 \\ 
RankELM (pointwise) & 0.80555556 & 1 \\ 
RankNet & 0.59154930 & 5 \\ 
Rank-PMBGP & 0.27272727 & 1 \\ 
RankRLS & 0.36842105 & 2 \\ 
RankSVM & 0.44957983 & 17 \\ 
RankSVM-Primal & 0.45911950 & 7 \\ 
RankSVM-Struct & 0.44670051 & 9 \\ 
RCP & 0.74074074 & 3 \\ 
Ridge Regression & 0.36477987 & 7 \\ 
RSRank & 0.62765957 & 4 \\ 
SmoothGrad & 0.38461538 & 2 \\ 
SmoothRank & 0.64150943 & 7 \\ 
SoftRank & 0.61111111 & 1 \\ 
SortNet & 0.56666667 & 4 \\ 
SparseRank & 0.79439252 & 4 \\ 
SVD-RankBoost & 0.55555556 & 3 \\ 
SVMMAP & 0.35911602 & 8 \\ 
SwarmRank & 0.09090909 & 1 \\ 
TGRank & 0.50000000 & 4 \\
\end{tabular}
\caption{Raw data of Normalised Winning Number comparison on NDCG@10}
\label{tab:raw_data_norm_winnum_NDCG10}
\end{table*}
